Stage 2 Yield Prediction

### 2016-02-11 Rmd/empirical-yields.Rmd
Developed several flavors of GAM-derived soy and maize grids, and adjusted them to FAO mean projected yields.

p_root <- lmisc::set_base_path()
p_clim <- fp(p_root, "external/input_devel/climate")
p_yield <- fp(p_root, "external/input_devel/yield")

@@

# Fit model
## Exploratory plots
```{r, eval = FALSE}
plot(prov)
regdt[CROP == "maize", points(x, y, pch = 16, cex = 0.5)]
regdt[CROP == "maize" & YLDS > 8000, 
      points(x, y, pch = 16, cex = 0.5, col = "red")]
regdt[CROP == "maize" & YLDS > 8000, 
      points(x, y, pch = 16, cex = 0.5, col = "red")]
regdt[CROP == "soybean" & YLDS > 1700, 
      points(x, y, pch = 16, cex = 0.5, col = "blue")]

# Prune out yields > 8000 maize > 1700 soybean in subsistence case
mzfilt <- regdt[CROP == "soybean" & YLDS > 1700, unique(.SD), 
                .SDcols = c("x", "y", "SOL", "WTH", "Zone")]
soyfilt <- regdt[CROP == "maize" & YLDS > 8000, unique(.SD), 
                 .SDcols = c("x", "y", "SOL", "WTH", "Zone")]
regnew <- regdt[!x %in% soyfilt$x | !y %in% soyfilt$y]
# regnew[CROP == "maize", points(x, y, pch = 16, cex = 0.5, col = "green")]

@@

# summary(lm(YLDS ~ poly(MAP, 2), data = regnew[CROP == "maize", ]))
# summary(lm(YLDR ~ poly(MSP, 2), data = regnew[CROP == "maize", ]))
regnew[CROP == "maize", plot(MAP, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "soybean", plot(MAP, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "soybean", plot(MAP, YLDR, pch = 16, cex = 0.5)]
regnew[CROP == "soybean", plot(MSP, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "soybean", plot(MSP, YLDR, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(FP, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(MSP, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(MSP, YLDR, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(sloc, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(sloc, YLDR, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(slcl, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(slcl, YLDR, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(slsi, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(slsi, YLDR, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(sbdm, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(sbdm, YLDR, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(slhw, YLDS, pch = 16, cex = 0.5)]  # pH looks pred
regnew[CROP == "maize", plot(slhw, YLDR, pch = 16, cex = 0.5)]  # pH looks pred
regnew[CROP == "maize", plot(GDD, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(KDD, YLDS, pch = 16, cex = 0.5)]
# regnew[CROP == "maize", plot(log(KDD), YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(NKJ, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(NKF, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(ATMX, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(STMX, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(STMX, YLDR, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(SSRT, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(SSRM, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(ASRT, YLDS, pch = 16, cex = 0.5)]
regnew[CROP == "maize", plot(ASRM, YLDS, pch = 16, cex = 0.5)]

regnew[, round(cor(.SD), 2), .SDcols = names(regnew)[-c(1:13)]]

summary(lm(YLDS ~ poly(sbdm, 2) + poly(slhw, 2), 
           data = regnew[CROP == "maize", ]))
summary(lm(YLDS ~ poly(slhw, 2), data = regnew[CROP == "maize", ]))
summary(lm(YLDS ~ poly(sbdm, 2), data = regnew[CROP == "maize", ]))
summary(lm(YLDS ~ poly(KDD, 2), data = regnew[CROP == "maize", ]))
summary(lm(YLDR ~ poly(STMX, 2), data = regnew[CROP == "maize", ]))
summary(lm(YLDS ~ poly(STMX, 2), data = regnew[CROP == "maize", ]))
summary(lm(YLDS ~ KDD, data = regnew[CROP == "maize", ]))
summary(lm(YLDS ~ poly(GDD, 2), data = regnew[CROP == "maize", ]))

# p <- "sbdm"; d <- "YLDS"
# regnew[CROP == "maize", {
#   lm1 <- lm(get(d) ~ get(p))
#   lm2 <- lm(get(d) ~ poly(get(p), 2))
#   plot(get(p), get(d), pch = 16, cex = 0.1)
#   abline(lm1)
#   dum <- data.frame(floor(min(get(p))):ceiling(max(get(p))))
#   colnames(dum) <- p
#   lines(dum[, 1], predict(lm2, newdata = dum), col = "red")
#   summary(lm1)
#   # summary(lm2)
# }]

reg_plotter <- function(dep, pred) {
  lm1 <- lm(dep ~ pred)
  lm2 <- lm(dep ~ poly(pred, 2))
  plot(pred, dep, pch = 16, cex = 0.1)
  abline(lm1)
  prng <- c(floor(min(pred)), ceiling(max(pred)))
  dum <- data.frame(seq(prng[1], prng[2], by = diff(prng) / 100))
  # dum <- data.frame(floor(min(pred)):ceiling(max(pred)))
  colnames(dum) <- "pred"
  preds <- predict(lm2, newdata = dum)
  lines(dum[, 1], preds, col = "red")
  mtext(round(summary(lm1)$adj.r.squared, 4), side = 3, adj = 0)
  mtext(round(summary(lm2)$adj.r.squared, 4), side = 3, adj = 0.5)
}
# regnew[CROP == "maize", reg_plotter(YLDR, GDD)]  # 
regnew[CROP == "maize", reg_plotter(YLDS, MAP)]  # P 0.045
regnew[CROP == "maize", reg_plotter(YLDS, MSP)]  # P 0.039
regnew[CROP == "maize", reg_plotter(YLDS, JP)]  # P 0.012
# regnew[CROP == "maize", reg_plotter(YLDS, JP - mean(JP))]  # P 0.012
regnew[CROP == "maize", reg_plotter(YLDS, FP)]  # P 0.005
regnew[CROP == "maize", reg_plotter(YLDS, OP)]  # P 0.003

regnew[CROP == "maize", reg_plotter(YLDS, slhw)]  # P 0.17
regnew[CROP == "maize", reg_plotter(YLDS, sloc)]  # P 0.266
# regnew[CROP == "maize", reg_plotter(YLDR, sloc)]  # P 
regnew[CROP == "maize", reg_plotter(YLDS, slcl)]  # P 0.185
regnew[CROP == "maize", reg_plotter(YLDS, sbdm)]  # 0.181
# mtax pairings
regnew[CROP == "maize", reg_plotter(YLDS, STMX)]  # P 0.07
regnew[CROP == "maize", reg_plotter(YLDS, ATMX)]  # P 0.056 
# NK
regnew[CROP == "maize", reg_plotter(YLDS, NKJ)]  # L 0.054
regnew[CROP == "maize", reg_plotter(YLDS, NKF)]  # P 0.027 
# GDD/KDD
regnew[CROP == "maize", reg_plotter(YLDS, GDD)]  # P 0.04
regnew[CROP == "maize", reg_plotter(YLDS, KDD)]  # L 0.027
# srad
regnew[CROP == "maize", reg_plotter(YLDS, SSRT)]  # P 0.012 
regnew[CROP == "maize", reg_plotter(YLDS, SSRM)]  # Same, picked up wrong one
regnew[CROP == "maize", reg_plotter(YLDS, ASRT)]  # P 0.0288 
regnew[CROP == "maize", reg_plotter(YLDS, ASRM)]  # P 0.0299

# best predictors look to be
# MAP, SLOC (but polynomial relationship odd), SLHW, slcl, sbdm, all good
# STMX (linear KDD as a possible alternate), GDD, ASRM

#
regnew[CROP == "maize", {
  lm1 <- lm(YLDS ~ poly(MAP, 2) + poly(slhw, 2) + poly(slcl, 2) +
              poly(sbdm, 2) + poly(GDD, 2) + KDD + poly(ASRM, 2))
  summary(lm1)
  # plot(YLDS, predict(lm1))
}]  # 0.4279

regnew[CROP == "maize", {
  lm1 <- lm(YLDS ~ poly(MAP, 2) + poly(slhw, 2) + poly(slcl, 2) +
              poly(sbdm, 2) + poly(GDD, 2) + poly(STMX, 2) + poly(ASRM, 2))
  summary(lm1)
  # plot(YLDS, predict(lm1))
}]  # 0.4199

regnew[CROP == "maize", {
  lm1 <- lm(YLDS ~ poly(MAP, 2) + poly(slhw, 2) + poly(sloc, 2) +
              poly(sbdm, 2) + poly(GDD, 2) + poly(STMX, 2) + poly(ASRM, 2))
  summary(lm1)
  # plot(YLDS, predict(lm1))
}]  # 0.4044 # SLOC doesn't give as much value, NS on linear

regnew[CROP == "maize", {
  lm1 <- lm(YLDS ~ poly(MAP, 2) + OP + poly(slhw, 2) + poly(slcl, 2) +
              poly(sbdm, 2) + poly(GDD, 2) + KDD + poly(ASRM, 2))
  summary(lm1)
  # plot(YLDS, predict(lm1))
}]  # 0.4293  # Doesn't add much

regnew[CROP == "maize", {
  lm1 <- lm(YLDS ~ poly(MAP, 2) + OP + poly(slhw, 2) + poly(slcl, 2) +
              poly(sbdm, 2) + poly(GDD, 2) + KDD + poly(ASRM, 2))
  summary(lm1)
  # plot(YLDS, predict(lm1))
}]  # 0.4293  # Oct precip add a tiny bit, significant

regnew[CROP == "maize", {
  lm1 <- lm(YLDS ~ poly(MAP, 2) + JP + poly(slhw, 2) + poly(slcl, 2) +
              poly(sbdm, 2) + poly(GDD, 2) + KDD + poly(ASRM, 2))
  summary(lm1)
  # plot(YLDS, predict(lm1))
}]  # 0.4312  # Jan precip adds more R2, but makes MAP linear NS

regnew[CROP == "maize", {
  lm1 <- lm(YLDS ~ poly(MAP, 2) + FP + poly(slhw, 2) + poly(slcl, 2) +
              poly(sbdm, 2) + poly(GDD, 2) + KDD + poly(ASRM, 2))
  summary(lm1)
  # plot(YLDS, predict(lm1))
}]  # 0.4374  # Feb precip even more R2, but makes MAP linear NS

regnew[CROP == "maize", {
  lm1 <- lm(YLDS ~ poly(MAP, 2) + OP + poly(slhw, 2) + poly(slcl, 2) +
              poly(sbdm, 2) + poly(GDD, 2) + KDD + poly(ASRM, 2) + x + y)
  summary(lm1)
  plot(YLDS, predict(lm1))
}]  # 0.4301  # Oct precip add a tiny bit, significant

# regnew[CROP == "maize", {
#   gam1 <- bam(YLDS ~ poly(MAP, 2) + OP + poly(slhw, 2) + poly(slcl, 2) +
#               poly(sbdm, 2) + poly(GDD, 2) + KDD + poly(ASRM, 2) + s(x, y), 
#              family = gaussian(link = "log"), method = "ML")
#   summary(gam1)
#   # plot(YLDS, predict(lm1))
# }]  # 0.4301  # Oct precip add a tiny bit, significant

@@

# regred[, c("Y10S", "Y90S") := as.integer(0)]

regmu <- regnew[CROP == "maize", lapply(.SD, mean), 
                by = list(CROP, WTH, Zone, SOL), 
                .SDcols = names(regnew)[c(3:4, 11:ncol(regnew))]]
regmu[, YST := "mu"]
# regnew[CROP == "maize" & Zone == "Zone2a" & WTH == "AABS" & 
#          SOL == "WI_CMZR003", mean(YLDS)]
qs <- function(x, y, ptile) {
  DF <- cbind(1:length(x), x, y)
  DF <- DF[order(DF[, 2]), ]
  DF[round(nrow(DF) * ptile), 3]
}

@@

a <- regnew[CROP == "maize" & Zone == "Zone3" & WTH == "AEQA" & 
            SOL == "WI_RGTZ054", YLDS]
b <- regnew[CROP == "maize" & Zone == "Zone3" & WTH == "AEQA" & 
            SOL == "WI_RGTZ054", mid]
qs(a, b, 0.9)
sort(a)

# Select out quantile values
m10 <- regred[,
  qs(YLDS, mid2, 0.1), by = list(CROP, WTH, Zone, SOL)
][, V1]
m90 <- regred[,
  qs(YLDS, mid2, 0.9), by = list(CROP, WTH, Zone, SOL) 
][, V1]

@@

regred2[CROP == "maize", reg_plotter(YLDS, MAP)]  # P 0.071
regred2[CROP == "maize", reg_plotter(YLDS, MSP)]  # P 0.039
regred2[CROP == "maize", reg_plotter(YLDS, JP)]  # P 0.020
regred2[CROP == "maize", reg_plotter(YLDS, FP)]  # P 0.017
regred2[CROP == "maize",  summary(lm(YLDS ~ poly(FP, 2)))]
regred2[CROP == "maize", reg_plotter(YLDS, 100 - slcl + slsi)]  # P 0.102
regred2[CROP == "maize", reg_plotter(YLDS, slcl)]  # P 0.1879
regred2[CROP == "maize", reg_plotter(YLDS, slsi)]  # P 0.03

regred2[CROP == "maize", {
  lm1 <- lm(YLDS ~ poly(MAP, 2) + OP + poly(slhw, 2) + poly(slcl, 2) +
              poly(sbdm, 2) + poly(GDD, 2) + KDD + poly(ASRM, 2) + x + y)
  summary(lm1)
  # plot(YLDS, predict(lm1))
}]  # 0.4301  # Oct precip add a tiny bit, significant

regred2[CROP == "maize" & YST == "mu", {
  lm1 <- lm(YLDS ~ poly(MAP, 2) + OP + poly(slhw, 2) + poly(slcl, 2) +
              poly(sbdm, 2) + poly(GDD, 2) + KDD + poly(ASRM, 2) + x + y)
  summary(lm1)
  # plot(YLDS, predict(lm1))
}]  # 0.4301  # Oct precip add a tiny bit, significant

regred2[CROP == "maize", {
  lm1 <- lm(YLDS ~ poly(MAP, 2) + poly(JP, 2) + poly(slhw, 2) + poly(slcl, 2) +
              poly(sbdm, 2) + poly(GDD, 2) + KDD + poly(ASRM, 2))
  summary(lm1)
  # plot(YLDS, predict(lm1))
}]  # 0.4301  # Oct precip add a tiny bit, significant

regred2[CROP == "maize", {
  lm1 <- lm(YLDS ~ poly(MAP, 2) + poly(JP, 2) + poly(slhw, 2) + poly(sloc, 2) +
              poly(sbdm, 2) + poly(GDD, 2) + KDD + poly(ASRM, 2))
  summary(lm1)
  # plot(YLDS, predict(lm1))
}]  # 0.4301  # Oct precip add a tiny bit, significant

regred2[CROP == "maize", {
  gam1 <- gam(YLDS ~ s(MAP) + s(JP) + s(slhw) + s(slcl) + (sbdm) + s(GDD) +
                KDD + s(ASRM), 
            family = gaussian(link = "log"), method = "ML")
}]

gam1 <- gam(YLDS ~ s(MAP, k = 3) + s(JP, k = 3) + s(slhw, k = 3) + 
              s(slcl, k = 3) + s(sbdm, k = 3) + s(GDD, k = 3) + KDD + 
              s(ASRM, k = 3), family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam2 <- gam(YLDS ~ poly(MAP, 2) + poly(JP, 2) + poly(slhw, 2) + 
              poly(slcl, 2) + poly(sbdm, 2) + poly(GDD, 2) + KDD + 
              poly(ASRM, 2), family = gaussian(link = "log"), method = "REML", 
            data = regred2[CROP == "maize"])
gam3 <- gam(YLDS ~ poly(MAP, 2) + poly(JP, 2) + poly(slhw, 2) + 
              poly(slcl, 2) + poly(sbdm, 2) + poly(GDD, 2) + KDD + 
              poly(ASRM, 2) + s(x, y), 
            family = gaussian(link = "log"), method = "REML", 
            data = regred2[CROP == "maize"])
gam4 <- gam(YLDS ~ poly(MAP, 2) + poly(JP, 2) + poly(slhw, 2) + 
              poly(slcl, 2) + poly(sbdm, 2) + poly(GDD, 2) + KDD + 
              s(x, y), family = gaussian(link = "log"), method = "REML", 
            data = regred2[CROP == "maize"])
gam5 <- gam(YLDS ~ poly(MAP, 2) + poly(JP, 2) + poly(slhw, 2) + 
              poly(slcl, 2) + poly(sbdm, 2) + poly(GDD, 2) + KDD, 
            family = gaussian(link = "log"), method = "REML", 
            data = regred2[CROP == "maize"])
gam6 <- gam(YLDS ~ poly(MAP, 2) + poly(JP, 2) + poly(slhw, 2) + 
              poly(slcl, 2) + poly(GDD, 2) + KDD, 
            family = gaussian(link = "log"), method = "REML", 
            data = regred2[CROP == "maize"])
gam7 <- gam(YLDS ~ poly(MAP, 2) + poly(slhw, 2) + 
              poly(slcl, 2) + poly(GDD, 2) + KDD, 
            family = gaussian(link = "log"), method = "REML", 
            data = regred2[CROP == "maize"])
gam8 <- gam(YLDS ~ poly(MAP, 2) + slhw +  poly(slcl, 2) + poly(GDD, 2) + KDD, 
            family = gaussian(link = "log"), method = "REML", 
            data = regred2[CROP == "maize"])
gam9 <- gam(YLDS ~ poly(MAP, 2) + slhw + poly(slcl, 2) + 
              poly(100 - (slcl + slsi), 2) + poly(GDD, 2) + KDD, 
            family = gaussian(link = "log"), method = "REML", 
            data = regred2[CROP == "maize"])
gam10 <- gam(YLDS ~ poly(MAP, 2) + slhw + poly(slcl, 2) + 
               poly(sloc, 2) + poly(GDD, 2) + KDD, 
             family = gaussian(link = "log"), method = "REML", 
             data = regred2[CROP == "maize"])
gam11 <- gam(YLDS ~ poly(MAP, 2) + slhw + poly(slcl, 2) + 
               sloc + poly(GDD, 2) + KDD, 
             family = gaussian(link = "log"), method = "REML", 
             data = regred2[CROP == "maize"])
gam12 <- gam(YLDS ~ poly(MAP, 2) + slhw + poly(slcl, 2) + 
               sloc + poly(GDD, 2) + KDD + s(x, y), 
             family = gaussian(link = "log"), method = "REML", 
             data = regred2[CROP == "maize"])

summary(gam3)
plot.gam(gam3, residuals = TRUE, se = TRUE, all.terms = TRUE, pages = 1)
summary(gam4)
plot.gam(gam4, residuals = TRUE, se = TRUE, all.terms = TRUE, pages = 1)
summary(gam5)
plot.gam(gam5, residuals = TRUE, se = TRUE, all.terms = TRUE, pages = 1)
summary(gam6)
plot.gam(gam6, residuals = TRUE, se = TRUE, all.terms = TRUE, pages = 1)
summary(gam7)
plot.gam(gam7, residuals = TRUE, se = TRUE, all.terms = TRUE, pages = 1)
summary(gam8)
plot.gam(gam8, residuals = TRUE, se = TRUE, all.terms = TRUE, pages = 1)
summary(gam9)
plot.gam(gam9, residuals = TRUE, se = TRUE, all.terms = TRUE, pages = 1)
summary(gam10)
plot.gam(gam10, residuals = TRUE, se = TRUE, all.terms = TRUE, pages = 1)
summary(gam11)  # This one or
plot.gam(gam11, residuals = TRUE, se = TRUE, all.terms = TRUE, pages = 1)
summary(gam12)  # of this one, with smooth x, y terms
plot.gam(gam12, residuals = TRUE, se = TRUE, all.terms = TRUE, pages = 1)

par(mfrow = c(2, 2))
plot(regred2[CROP == "maize", YLDS], predict(gam11, type = "response"))
plot(regred2[CROP == "maize", YLDS], predict(gam12, type = "response"))
plot(regred2[CROP == "maize", YLDS], predict(gam4, type = "response"))

>>>>

p_root <- lmisc::set_base_path()
p_clim <- fp(p_root, "external/input_devel/climate")
p_yield <- fp(p_root, "external/input_devel/yield")
p_sgrids <- fp(p_root, "external/input_devel/soil") 
p_basedat <- paste0("/Users/lestes/Dropbox/projects/agroEcoTradeoff/external/",
                    "base_data/")
p_cropland <- full_path(p_root, "external/input_devel/cropland")

# Read in Zambia grid
mgrid <- raster(full_path(p_basedat, "ZA-grid.tif"))

@@

# Fit model
## Exploratory plots
```{r, eval = FALSE}
plot(prov)
regdt[CROP == "maize", plot(DJFMP, YLDR)]
regdt[CROP == "maize", plot(DJFMP, YLDS)]
regdt[CROP == "soy", plot(DJFMP, YLDR)]
regdt[CROP == "soy", plot(DJFMP, YLDS)]
regdt[CROP == "maize", mean(YLDR)]
regdt[CROP == "maize", mean(YLDS)]
regdt[CROP == "soy", mean(YLDR)]
regdt[CROP == "soy", mean(YLDS)]

regnew <- copy(regdt)
# regdt[CROP == "maize", points(x, y, pch = 16, cex = 0.5)]
# regdt[CROP == "maize" & YLDS > 15000, 
#       points(x, y, pch = 16, cex = 0.5, col = "red")]
# regdt[CROP == "soy", plot(MAP, YLDR)]
# regdt[CROP == "soy" & YLDS > 1700, 
#       points(x, y, pch = 16, cex = 0.5, col = "blue")]

# Prune out yields > 8000 maize > 1700 soy in subsistence case
# soyfilt <- regdt[CROP == "soy" & YLDS > 1700, unique(.SD), 
#                 .SDcols = c("x", "y", "SOL", "WTH", "Zone")]
# mzfilt <- regdt[CROP == "maize" & YLDS > 9000, unique(.SD), 
#                 .SDcols = c("x", "y", "SOL", "WTH")]
# # regnew <- regdt[!x %in% soyfilt$x | !y %in% soyfilt$y]
# regnew <- regdt[!x %in% mzfilt$x | !y %in% mzfilt$y]
# regnew[CROP == "maize", points(x, y, pch = 16, cex = 0.5, col = "green")]

@@

# summary(lm(YLDS ~ poly(MAP, 2), data = regnew[CROP == "maize", ]))
# summary(lm(YLDR ~ poly(MSP, 2), data = regnew[CROP == "maize", ]))

reg_plotter <- function(dep, pred) {
  lm1 <- lm(dep ~ pred)
  lm2 <- lm(dep ~ poly(pred, 2))
  plot(pred, dep, pch = 16, cex = 0.1)
  abline(lm1)
  prng <- c(floor(min(pred)), ceiling(max(pred)))
  dum <- data.frame(seq(prng[1], prng[2], by = diff(prng) / 100))
  # dum <- data.frame(floor(min(pred)):ceiling(max(pred)))
  colnames(dum) <- "pred"
  preds <- predict(lm2, newdata = dum)
  lines(dum[, 1], preds, col = "red")
  mtext(round(summary(lm1)$adj.r.squared, 4), side = 3, adj = 0)
  mtext(round(summary(lm2)$adj.r.squared, 4), side = 3, adj = 0.5)
}

# Rainfall
regnew[CROP == "maize", reg_plotter(YLDS, MAP)] ##
regnew[CROP == "maize", reg_plotter(YLDS, MSP)] #
regnew[CROP == "maize", reg_plotter(YLDS, DJFMP)] ###
regnew[CROP == "maize", reg_plotter(YLDS, JFMP)] #
regnew[CROP == "maize", reg_plotter(YLDS, FP)]  
regnew[CROP == "maize", reg_plotter(YLDS, OP)]

# soil
regnew[CROP == "maize", reg_plotter(YLDS, SLHW)]  ###
regnew[CROP == "maize", reg_plotter(YLDS, SLOC)]  # 
regnew[CROP == "maize", reg_plotter(YLDS, SLCL)]  ## 
regnew[CROP == "maize", reg_plotter(YLDS, SBDM)]  ##

# TEMP
regnew[CROP == "maize", reg_plotter(YLDS, TMU)]  ## 
regnew[CROP == "maize", reg_plotter(YLDS, STMX)]  # 
regnew[CROP == "maize", reg_plotter(YLDS, ATMX)]  #
regnew[CROP == "maize", reg_plotter(YLDS, GDD)]  # 
regnew[CROP == "maize", reg_plotter(YLDS, KDD)]  
regnew[CROP == "maize", reg_plotter(YLDS, NKJ)]  ##
regnew[CROP == "maize", reg_plotter(YLDS, NKF)]  ##

# srad
regnew[CROP == "maize", reg_plotter(YLDS, ASRT)]  
regnew[CROP == "maize", reg_plotter(YLDS, ASRM)]  
regnew[CROP == "maize", reg_plotter(YLDS, SSRMI)]  ##
regnew[CROP == "maize", reg_plotter(YLDS, SSRMII)]  # 
regnew[CROP == "maize", reg_plotter(YLDS, SSRMIII)] #

@@

# regred[, c("Y10S", "Y90S") := as.integer(0)]
# regred[CROP == "maize" & SOL == "HC_GEN0010" & WTH == "KALA", mean(GDD)]
regmu <- regred[CROP == "maize", lapply(.SD, mean), 
                by = list(CROP, x, y, WTH, SOL), 
                .SDcols = names(regred)[c(8:ncol(regred))]]
regmu[, YST := "mu"]
# regnew[CROP == "maize" & Zone == "Zone2a" & WTH == "AABS" & 
#          SOL == "WI_CMZR003", mean(YLDS)]
qs <- function(x, y, ptile) {
  DF <- cbind(1:length(x), x, y)
  DF <- DF[order(DF[, 2]), ]
  DF[round(nrow(DF) * ptile), 3]
}

@@

# a <- regnew[CROP == "maize" & WTH == "AEQA" & SOL == "WI_RGTZ054", YLDS]
# b <- regnew[CROP == "maize" & WTH == "AEQA" & SOL == "WI_RGTZ054", mid]
# qs(a, b, 0.9)
# sort(a)

# Select out quantile values
m10 <- regred[,
  qs(YLDS, mid2, 0.1), by = list(CROP, x, y, WTH, SOL)
][, V1]
m90 <- regred[,
  qs(YLDS, mid2, 0.9), by = list(CROP, x, y, WTH, SOL)
][, V1]

@@

# Fit gams
regred2[, round(cor(.SD), 2), 
        .SDcols = c("MAP", "MSP", "DJFMP", "JFMP", "JP", "FP", "OP")]  # 0.7
#        MAP  MSP DJFMP  JFMP    JP    FP    OP
# MAP   1.00 0.91  0.91  0.88  0.59  0.57  0.23
# MSP   0.91 1.00  0.90  0.83  0.71  0.63  0.06
# DJFMP 0.91 0.90  1.00  0.96  0.73  0.66 -0.02
# JFMP  0.88 0.83  0.96  1.00  0.73  0.73 -0.03
# JP    0.59 0.71  0.73  0.73  1.00  0.31 -0.07
# FP    0.57 0.63  0.66  0.73  0.31  1.00 -0.09
# OP    0.23 0.06 -0.02 -0.03 -0.07 -0.09  1.00
regred2[, round(cor(.SD), 2),  
        .SDcols = c("TMU", "GDD", "KDD", "NKF", "NKJ", "STMX", "ATMX")]
#       TMU  GDD  KDD  NKF  NKJ STMX ATMX
# TMU  1.00 0.87 0.45 0.80 0.87 0.95 0.90
# GDD  0.87 1.00 0.27 0.65 0.71 0.80 0.89
# KDD  0.45 0.27 1.00 0.31 0.48 0.42 0.34
# NKF  0.80 0.65 0.31 1.00 0.87 0.81 0.78
# NKJ  0.87 0.71 0.48 0.87 1.00 0.86 0.80
# STMX 0.95 0.80 0.42 0.81 0.86 1.00 0.90
# ATMX 0.90 0.89 0.34 0.78 0.80 0.90 1.00
regred2[, round(cor(.SD), 2),  
        .SDcols = c("TMU", "SSRMI", "SSRMIII", "MAP", "DJFMP", "JFMP", "GDD")]
#           TMU SSRMI SSRMIII   MAP DJFMP  JFMP   GDD
# TMU      1.00  0.70    0.69 -0.65 -0.62 -0.60  0.87
# SSRMI    0.70  1.00    0.91 -0.69 -0.60 -0.58  0.40
# SSRMIII  0.69  0.91    1.00 -0.64 -0.59 -0.61  0.45
# MAP     -0.65 -0.69   -0.64  1.00  0.91  0.88 -0.45
# DJFMP   -0.62 -0.60   -0.59  0.91  1.00  0.96 -0.47
# JFMP    -0.60 -0.58   -0.61  0.88  0.96  1.00 -0.43
# GDD      0.87  0.40    0.45 -0.45 -0.47 -0.43  1.00

regred2[, round(cor(.SD), 2), 
        .SDcols = c("SLOC", "SBDM", "SLCL", "SLHW", "SLSI")]  
#       SLOC  SBDM  SLCL  SLHW  SLSI
# SLOC  1.00 -0.67  0.53 -0.30  0.03
# SBDM -0.67  1.00 -0.77  0.34 -0.26
# SLCL  0.53 -0.77  1.00 -0.64 -0.09
# SLHW -0.30  0.34 -0.64  1.00  0.36
# SLSI  0.03 -0.26 -0.09  0.36  1.00

gam1 <- gam(YLDS ~ s(MAP, k = 3)  + s(TMU, k = 3) + s(SLHW, k = 3) + 
              s(SLCL, k = 3) + s(SLOC, k = 3) + 
              s(SSRMI, k = 3), family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])

gam2 <- gam(YLDS ~ s(MAP, k = 3) + s(TMU, k = 3) + s(SLHW, k = 3) + 
              s(SLCL, k = 3) + s(SLOC, k = 3), 
            family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])

gam3 <- gam(YLDS ~ poly(MAP, 2) + s(TMU, k = 3) + s(SLHW, k = 3) + 
              s(SLCL, k = 3) + s(SLOC, k = 3), 
            family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam4 <- gam(YLDS ~ poly(MAP, 2) + poly(TMU, 2) + s(SLHW, k = 3) + 
              s(SLCL, k = 3) + s(SLOC, k = 3), 
            family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam5 <- gam(YLDS ~ poly(MAP, 2) + poly(TMU, 2) + s(SLHW, k = 3) + 
              s(SLCL, k = 3), 
            family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam6 <- gam(YLDS ~ poly(DJFMP, 2) + poly(TMU, 2) + s(SLHW, k = 3) + 
              s(SLCL, k = 3), 
            family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam7 <- gam(YLDS ~ poly(DJFMP, 2) + poly(TMU, 2) + poly(SLHW, 2) + 
              s(SLCL, k = 3), 
            family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam8 <- gam(YLDS ~ poly(DJFMP, 2) + poly(TMU, 2) + poly(SLHW, 2) + 
              poly(SLCL, 2), 
            family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam9 <- gam(YLDS ~ poly(MSP, 2) + poly(TMU, 2) + poly(SLHW, 2) + 
              poly(SLCL, 2), 
            family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam10 <- gam(YLDS ~ poly(JFMP, 2) + poly(TMU, 2) + poly(SLHW, 2) + 
              poly(SLCL, 2), family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam11 <- gam(YLDS ~ poly(JFMP, 2) + poly(TMU, 2) + poly(SLHW, 2) + 
              poly(SLCL, 2) + s(x, y), 
             family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam12 <- gam(YLDS ~ poly(JFMP, 2) + poly(TMU, 2) + poly(SLHW, 2) + 
              poly(SLCL, 2) + poly(SLOC, 2) + s(x, y), 
             family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam13 <- gam(YLDS ~ poly(JFMP, 2) + poly(TMU, 2) + poly(SSRMI, 2) + 
               poly(SLHW, 2) + poly(SLCL, 2) + s(x, y), 
             family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam14 <- gam(YLDS ~ poly(JFMP, 2) + poly(TMU, 2) + poly(SSRMI, 2) + 
               poly(SLHW, 2) + poly(SLCL, 2) + s(x, y), 
             family = gaussian(link = "log"), method = "ML", 
            data = regnew[CROP == "maize"])
gam15 <- gam(YLDS ~ poly(JFMP, 2) + poly(TMU, 2) + poly(SSRMI, 2) + 
               poly(SLHW, 2) + poly(SLCL, 2) + s(x, y), 
             family = gaussian(link = "log"), method = "ML", 
            data = regred2[YST == "mu"])
gam16 <- gam(YLDS ~ s(JFMP, k = 3)  + s(TMU, k = 3) + s(SLHW, k = 3) + 
               s(SLCL, k = 3) + s(SSRMI, k = 3), 
             family = gaussian(link = "log"), method = "ML", 
             data = regred2[CROP == "maize"])
gam17 <- gam(YLDS ~ poly(JFMP, 2) + poly(GDD, 2) + poly(SSRMI, 2) + 
               poly(SLHW, 2) + poly(SLCL, 2) + s(x, y), 
             family = gaussian(link = "log"), method = "ML", 
            data = regred2[CROP == "maize"])
gam18 <- gam(YLDS ~ poly(JFMP, 2) + poly(GDD, 2) + poly(SSRMI, 2) + 
               poly(SLHW, 2) + poly(SLCL, 2) + s(x, y), 
             family = gaussian(link = "log"), method = "ML", 
            data = regnew[CROP == "maize"])
